A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-12-27 paper/reviews/response.tex

\maketitle

%\tableofcontents

\thispagestyle{empty}
%\bigskip

The thoughtful comments from the two reviewers are much appreciated.  Below we respond to their concerns.  The paper was revised based on these comments and concerns, and some additional edits were made to improve readability.  (A colored \LaTeX difference PDF is included to show the extent of the revisions.)  Our revisions have not significantly lengthened the paper.

@@

\section{Responses to Referee 1}

%%% ELB CONFIDENTIAL  I am guessing this is Tai himself.

\begin{review}
This paper is about using multilevel algorithm to solve nonlinear problems with constraints. Many real-world applications need to solve problem of this kind. Thus, the fast algorithm proposed here is of great importance.

This work proposed to improve the CD (constraint decomposition) method of [32] in several aspects. The new techniques are innovative (see detailed comments below) and show very good performances in numerical experiments report in this paper. I strongly suggest accepting this work for SISC after some minor revisions suggested below.
\end{review}

\short{This summary is accurate, and the expression of support is appreciated!}

\begin{review}
The reasons that I suggest accepting this paper are based on the following observations:

@@

1. This paper proposed a new way to decompose the constraint set as shown in section 5. This is a good and innovative idea. In the original algorithm of [32], all the decompositions need to go to the finest level. With this new technique, only the nearest level of grid needs to be involved. This is a great advantage.

2. Another advantage of the method proposed in this paper is to use FAS (full approximation Scheme) to solve the subproblems over the different levels, while the original scheme of [32] needs to solve a nonlinear problems over the different grid levels that is projected from the finest mesh and also exactly (even though, approximation solver can be considered as in Tai-Espedal (SINUM 1998). This is making the coarse grid solving much fast and cheaper.

3. This paper proposed to use the algorithm for general monotone nonlinear problems with constraints, while the algorithm proposed in [32] is only for minimization problems. The operator from convex minimization problems is monotone, but there are many monotone operators that are not from minimization problems as shown in Example 2.5 and 2.6 of this work.
\end{review}

\short{The reviewer points out our new algorithm's avoidance of the ``need to go to the finest level.''  This idea is now a sentence in our revised Introduction.  We also appreciate the pointer to Tai \& Espedal (1998), which shows convergence of a space decomposition method even each subspace solver is only approximate.  If we could supply a convergence proof this would be relevant, but we do not see how to do this currently.}

@@

\begin{review}
The weak point of this work is that there is no convergence proof for the proposed algorithms. Intuitively, the constraint decomposition given in this paper is much tighter. It would give a better correction during the iterations, but this is not shown theoretically nor numerically.
\end{review}

\begin{response}
We agree that this is the weakest point of the work.  Sadly, a convergence proof is not yet available.  We believe that the algorithm is sufficiently powerful as to be worthwhile publishing, and that our numerical demonstrations adequately support this claim.
\end{response}

@@

\begin{review}
The proposed FMG solver is an optimal solver as claimed by the authors. It also improves CD method of [32] in several aspects. The authors need to supply comparisons between the two methods in the numerical section.
\end{review}

\short{Our numerical demonstrations support the claim of optimality, and the reviewer seems to agree.  Regarding the need to supply comparisons, we think that our already-included comparison to results from [22] (Graeser \& Kornhuber, 2009), who implemented the [32] (Tai, 2003) method using a constraint decomposition like ours, are more relevant.  (This comparison is discussed near the end of Example 8.1.)  Our convergence rates are much better than those in [32], and comparable to those in [22], with our rates about $0.10$ compared to $>0.70$ for [32] on the same ``ball'' problem at comparable resolution; smaller numbers are better.  However, the improvement on this simplest Laplacian obstacle problem is largely our better smoother.}

### 2023-12-28 paper/fascd.tex
put in a convergence figure, in response to reviewer 1

@@

%REGENERATE using reproduce/table2.py at git@bitbucket.org:pefarrell/fascd.git
\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{asymprates.pdf}
\caption{V-cycle asymptotic convergence rates in Example \ref{ex:results:classical}.}
\label{fig:results:asymp}
\end{figure}

>>>>

The ball problem has an accurately-known solution $u\in W^{2,\infty}(\Omega)$\cite{Bueler2021,Tai2003}.  Figure \ref{fig:results:convergence} shows that the $L^2$ convergence rate is $O(h^2)$ as expected for $P_1$ elements FIXME: CITE CIARLET? GLOWINSKI?

@@

%REGENERATE using reproduce/table2.py at git@bitbucket.org:pefarrell/fascd.git
\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{asymprates.pdf}
\caption{V-cycle asymptotic rates in Example \ref{ex:results:classical}.}
\label{fig:results:asymp}
\end{figure}

%REGENERATE using reproduce/table2.py at git@bitbucket.org:pefarrell/fascd.git
\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{convergence.pdf}
\caption{Convergence rate for the ball problem in Example \ref{ex:results:classical}.}
\label{fig:results:convergence}
\end{figure}
